\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-04 chapters/1_intro.tex
Update figures, conclusions, and plots

\begin{figure*}[t]
\centering
\includegraphics[width=0.5\textwidth]{figs/intro_image_v4.pdf} % left bottom right top
\caption{\TODO{Redo figure}\algname{} example. \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black). (\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph. \TODO{Check if avg is correct}
\label{fig:intro_figure}}
\end{figure*}

@@

        \end{tabular}
    \end{subtable} 
    \caption{Clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. New algorithms are highlighted in yellow (hierarchical clustering with constraints, HCC). Algorithms typeset in bold font define an ultrametric on the graph (see Eq.~\ref{eq:UM_def}). Algorithms included in the green box, are weight-shift invariant (see Prop.~\ref{prop:weight_shift_invariant}). 
    We denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i, S_j$. } 
    \label{tab:linkage-criteria}
\end{table*}

@@

In this paper, we propose a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Table~\ref{tab:linkage-criteria}). 
We then formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before. By analyzing their theoretical properties, we also show which one of them define ultrametrics on the graph.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.98\textwidth]{figs/intro_image_v5.pdf} % left bottom right top
\caption{\textbf{(a)} Some iterations of \algname{}, the proposed Generalized Agglomerative Algorithm for Signed Graph Partitioning, on a toy graph with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (average and sum linkage methods are shown). \textbf{(b)} List of linkage criteria used in this paper (see definitions in Table~\ref{tab:linkage-criteria} below), demonstrated on two small clusters.  \textbf{(c)} Application of \algname{} to instance segmentation: we show raw data from the CREMI 2016 neuron-segmentation challenge and some predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(d)} \algname{} agglomeration order for sum and average linkage: we show which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black).
\label{fig:intro_figure}}
\end{figure*}

@@

        \end{tabular}
    \end{subtable} 
    \caption{Clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. New algorithms are highlighted in yellow (hierarchical clustering with constraints, HCC). Algorithms typeset in bold font define an ultrametric on the graph (see Eq.~\ref{eq:UM_def}). Algorithms included in the \TODO{green box}, are weight-shift invariant (see Prop.~\ref{prop:weight_shift_invariant}). 
    We denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i, S_j$. } 
    \label{tab:linkage-criteria}
\end{table*}

@@

In this paper, we propose a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\ref{fig:intro_figure}a-b and Table~\ref{tab:linkage-criteria}). 
We then formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before. By analyzing their theoretical properties, we also show which one of them define ultrametrics on the graph.

### 2021-03-04 chapters/3_algorithm.tex
Update figures, conclusions, and plots

\textbf{Linkage criteria and hierarchical trees} -- 
% We also denote as $S_u$ the cluster associated with node $u$ \TODO{Needed?}.
% We call two clusters $S,S'$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. 
Let the interaction $\interact(S,S')$ between two clusters $S,S'$ be defined as a function $\interact{}:2^{V} \times 2^{V} \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S$ and $S'$, i.e. ${(S \times S') \cap E}$. 
The linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
A \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary. However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} representing the merging order of an agglomerative algorithm, such that the leaves of the tree are in one-to-one correspondence with $V$. 
Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor $(u \vee v)\in T$ of nodes $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree. 
% \TODO{Here we talk about the algorithm already, so we could move it to next section and the flow could be better. But we need a tree in the alg. So we better do this later}
% Algorithm \ref{main_alg} returns a binary tree denoted by $T^*$.
Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (\TODO{Fig.~1}). We also define $\treeHeight(u,v)$ as the signed interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u\vee v)$: 
% Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
\begin{equation}\label{eq:def_dendr_interact}
\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T_{\mathrm{R}}[u \vee v]), \text{\texttt{leaves}}(T_{\mathrm{L}}[u \vee v]) \big)
\end{equation}
% \OPTIONAL{In other words, $h_T(u,v)$ and $\treeHeight(u,v)$ represent the \emph{dendrogram-height} and \emph{signed-interaction} associated to each $u \vee v$ node in the tree $T$ (see toy example in \TODO{Fig.~1}).}

>>>>

\textbf{Linkage criteria and hierarchical trees} -- 
% We also denote as $S_u$ the cluster associated with node $u$ \TODO{Needed?}.
% We call two clusters $S,S'$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. 
Let the interaction $\interact(S,S')$ between two clusters $S,S'$ be defined as a function $\interact{}:2^{V} \times 2^{V} \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S$ and $S'$, i.e. ${(S \times S') \cap E}$. 
The linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
A \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary. However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} representing the merging order of an agglomerative algorithm, such that the leaves of the tree are in one-to-one correspondence with $V$. 
Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor $(u \vee v)\in T$ of nodes $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree. 
% \TODO{Here we talk about the algorithm already, so we could move it to next section and the flow could be better. But we need a tree in the alg. So we better do this later}
% Algorithm \ref{main_alg} returns a binary tree denoted by $T^*$.
Given an agglomerative algorithm with merging tree $T$, let $h_T:T \rightarrow \mathbb{N}$ denote the \emph{dendrogram-height} of each $(u\vee v)\in T$, which is defined as the iteration number at which nodes $u,v\in V$ were merged by the algorithm (see example in Fig.~\ref{fig:intro_figure}b). We also define $\treeHeight(u,v)$ as the signed interaction $\interact{}(S,S')$ between the two clusters $S,S'$ that were merged at iteration $h_T(u\vee v)$: 
% Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
\begin{equation}\label{eq:def_dendr_interact}
\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T_{\mathrm{R}}[u \vee v]), \text{\texttt{leaves}}(T_{\mathrm{L}}[u \vee v]) \big)
\end{equation}
% \OPTIONAL{In other words, $h_T(u,v)$ and $\treeHeight(u,v)$ represent the \emph{dendrogram-height} and \emph{signed-interaction} associated to each $u \vee v$ node in the tree $T$ (see toy example in \TODO{Fig.~1}).}

### 2021-03-04 chapters/5_experiments_compare_rules.tex
Update figures, conclusions, and plots

\begin{figure}[t]
\centering
\includegraphics[width=0.47\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
        \caption{
ARAND errors (lower is better) on \emph{CREMI-gridGraph} clustering problems perturbed with structured noise. Average-linkage algorithms proved to be the most robust.
We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
% \algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}. \TODO{Define paramters SSB; explain percentile stuff (for both noise experiments), user ARAND-error}
}\label{fig:scores_structured_noise}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.47\textwidth,trim=0.2in 0.17in 0.2in 0.2in,clip]{./figs/noise_plots/noise_plots_adapted-rand_1.pdf}
        \caption{
ARAND errors (median values over 20 experiments, lower is better) on \emph{CREMI-gridGraph} clustering problems perturbed with structured noise. Average-linkage algorithms proved to be the most robust.
% We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
% \algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}. \TODO{Define paramters SSB; explain percentile stuff (for both noise experiments), user ARAND-error}
}\label{fig:scores_structured_noise}
\end{figure}

### 2021-03-04 chapters/5_experiments_intro.tex
Update figures, conclusions, and plots

        \begin{tabular}{l  c  r  c  c  | r r r r r r}
        % \toprule
        &&&&\multicolumn{1}{c}{}&\multicolumn{5}{c}{Multicut objective values associated to final clusterings:} \\
        Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$  & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
        \emph{Modularity Clustering} \cite{brandes2007modularity} & \emph{complete} & 6& 34-115 & 561-6555 & % \HollowBox & 
        -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{rag} & 100 & 156-3764 &  439-10970  & % \HollowBox 
        \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-rag} & 24 & 572-17k & 3381-107k & % \HollowBox & 
        \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
        % \emph{Knott-3D-300} & \emph{3D-rag} & 8& & & \HollowBox\\
        % \emph{Knott-3D-450}& \emph{3D-rag} & 8 & & & \HollowBox\\  
        \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k % & \CrossedBox 
        & \textbf{-1,112,287} & -1,112,286& -1,109,731 & -1,112,177 & -1,112,100\\ 
        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m %& \HollowBox 
        & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
        \emph{CREMI-gridGraph (OurCNN)} & \emph{gridGraph} & 15& 39m & 140m %& \CrossedBox 
        & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-rag} & 1& 90m & 650m % & \HollowBox 
        & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
        % \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\
        % \emph{CREMI-test....}\\\midrule
        % \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
        % \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\

@@

\textbf{Synthetic SSBM graphs} -- We first consider synthetic graphs generated by a signed stochastic block model (SSBM). We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$. Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) with standard deviation $\sigma$. To model noise, the sign of the edge weights is flipped independently with probability $\eta$.

@@

\textbf{Complete and Single Linkage} -- In our experiments, we included these two linkage methods as baselines to highlight the difficulty of the considered graph clustering problems. Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show the poor performances of these two linkage methods: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing graph connected components, often returned few big under-segmented clusters. HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters. 
% These algorithms are excluded from our next comparison experiments.

@@

    \caption{\textbf{Tables a-b:} Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods performed best. Measures shown are Adapted-Rand error (ARAND, lower is better), Variation of Information \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error, VOI-split for over-clustering error, lower is better). \textbf{Table c:} Current leading entries in the CREMI challenge leaderboard (March 2021). CREMI-score is given by geometric mean of (VOI-split + VOI-merge)  and adapted RAND error (lower is better).}

@@

@@

\textbf{Size of growing clusters: Sum vs Avg linkage} -- 
In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}. This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned the highest priority, because it is given by the sum of two highly attractive edge weights. And this will start a ``chain reaction'' where only a single cluster is agglomerated at the time. 
% This \emph{flooding strategy} in the agglomeration is not observed with other linkage methods, e.g. Average, which grow clusters of similar sizes in parallel.
In the following, we will show how this unique \emph{flooding strategy} of the sum-linkage methods can be both an advantage or a disadvantage, depending on the type of clustering problem.

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM (\TODO{parameters}).  Red and blue colors represent the ground truth labels of each initial graph node. Dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{}. \label{fig:dendrograms}}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.48\textwidth,trim=12 76 150 13, clip]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of three algorithms included in \algname{} on challenging parts of the CREMI dataset. \emph{Wrongly} segmented regions are highlighted in different warm colors. Red arrows point to wrongly split regions; yellow ones to merge errors. HC-Avg returned the best segmentation. Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  
\label{fig:failure_cases}}
\end{figure}
\begin{figure}[t]
\centering
\includegraphics[width=0.42\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
        \caption{
ARAND errors (lower is better) on synthetic graphs generated with SSBM (\TODO{parameters}). 
% The spectral clustering methods, SPONGE and SPONGE$_sym$, were given the true number of clusters as input. 
% Solid lines represent median values over \TODO{30} experiments. Values between the 25th and the 75th percentile are shown in shaded areas.
We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
%         Scores on SSBM graphs
% \algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.  The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
        } \label{fig:SSBM_scores}
\end{figure}

\textbf{Scores on SSBM graphs}  -- 
% can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$, followed then by HC-Avg and then MWS (see Fig.~\ref{fig:SSBM_scores}). Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results. 
In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size. On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities. From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (as compared to the avg-linkage method HC-Avg that grows small clusters and merge them only at the very end). This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here. Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise. In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently of the cluster sizes.

>>>>

        \begin{tabular}{l  c  r  c  c  | r r r r r r}
        % \toprule
        &&&& %\multicolumn{1}{c}{}
        &\multicolumn{5}{c}{Multicut objective values associated to final clusterings (lower is better)} \\
        Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$  & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
        \emph{Modularity Clustering} \cite{brandes2007modularity} & \emph{complete} & 6& 34-115 & 561-6555 & % \HollowBox & 
        -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{rag} & 100 & 156-3764 &  439-10970  & % \HollowBox 
        \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-rag} & 24 & 572-17k & 3381-107k & % \HollowBox & 
        \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
        % \emph{Knott-3D-300} & \emph{3D-rag} & 8& & & \HollowBox\\
        % \emph{Knott-3D-450}& \emph{3D-rag} & 8 & & & \HollowBox\\  
        \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k % & \CrossedBox 
        & \textbf{-1,112,287} & -1,112,286& -1,109,731 & -1,112,177 & -1,112,100\\ 
        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m %& \HollowBox 
        & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
        \emph{CREMI-gridGraph (OurCNN)} & \emph{gridGraph} & 15& 39m & 140m %& \CrossedBox 
        & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-rag} & 1& 90m & 650m % & \HollowBox 
        & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
        % \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\
        % \emph{CREMI-test....}\\\midrule
        % \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
        % \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\

@@

\textbf{Synthetic SSBM graphs} -- We first consider synthetic graphs generated by a signed stochastic block model (SSBM). We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$. Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma=0.1$. To model noise, the sign of the edge weights is flipped independently with probability $\eta$.

@@

\textbf{Complete and Single Linkage} -- In our experiments, we included these two linkage methods as baselines to highlight the difficulty of the considered graph clustering problems. Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show the poor performances of these two linkage methods: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters. HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters. 
% These algorithms are excluded from our next comparison experiments.

@@

    \caption{\textbf{Tables (a-b)}: Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods performed best. Measures shown are: Adapted-Rand error (ARAND, lower is better); Variation of Information (VOI) \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error and VOI-split for over-clustering error, lower values are better). \textbf{Table (c)}: Current leading entries in the CREMI challenge leaderboard (March 2021). CREMI-score is given by geometric mean of (VOI-split + VOI-merge)  and adapted RAND error (lower is better).}

@@

\begin{figure}[t]
\begin{subfigure}[t]{0.23\textwidth}
\includegraphics[width=\textwidth,trim=0.34in 0.34in 0.34in 0.34in,clip]{./figs/SSBM_scores/summary_SSBM_experiments_k20.pdf}
\caption{$k=20$, $p=0.1$}
\end{subfigure}\hfill
\begin{subfigure}[t]{0.23\textwidth}
\includegraphics[width=\textwidth,trim=0.34in 0.34in 0.34in 0.34in,clip]{./figs/SSBM_scores/summary_SSBM_experiments_k50.pdf}
\caption{$k=50$, $p=0.2$}
\end{subfigure}
        \caption{
ARAND errors (median values over 20 experiments, lower is better) on synthetic graphs generated with SSBM, with $N=10000$ nodes, edges added with probability $p$, and $k$ ground truth communities of random size. 
% The spectral clustering methods, SPONGE and SPONGE$_sym$, were given the true number of clusters as input. 
% Solid lines represent median values over \TODO{30} experiments. Values between the 25th and the 75th percentile are shown in shaded areas.
% We report median, 25th, and the 75th percentile values over \TODO{30} experiments.
%         Scores on SSBM graphs
% \algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions.  The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
        } \label{fig:SSBM_scores}
\end{figure}

\begin{figure}
\centering
% \includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order_OLD.png} % left bottom right top
\includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$, $p=0.05$, $\eta=0.1$, and $k=2$ communities of equal size).  Red and blue colors represent the true community of each initial node. At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{} (y-axis shows the iteration number). \label{fig:dendrograms}}
\end{figure}

@@

\textbf{Size of growing clusters: Sum vs Avg linkage} -- \TODO{Dendrogram}
In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}. This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights. This will then start a ``chain reaction'' where only a single cluster is agglomerated at the time. 
% This \emph{flooding strategy} in the agglomeration is not observed with other linkage methods, e.g. Average, which grow clusters of similar sizes in parallel.
In the following, we will show how this unique \emph{flooding strategy} of the sum-linkage methods can be both an advantage or a disadvantage, depending on the type of clustering problem.

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
\caption{Failure cases of three versions of \algname{} on challenging parts of the CREMI dataset. \emph{Wrongly} segmented regions are highlighted in different warm colors. Red arrows point to wrongly split regions; yellow ones to merge errors. HC-Avg returned the best segmentation. Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  
\label{fig:failure_cases}}
\end{figure}

\textbf{Scores on synthetic SSBM graphs}  -- 
% can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}). Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results. 
In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities. From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (as compared to the avg-linkage method HC-Avg that grows small clusters and merge them only at the very end). This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here. On the other hand, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise. In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see Appendix), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.

### 2021-03-04 chapters/6_conclusions.tex
Update figures, conclusions, and plots

% !TEX root = ../agglo_clust_review.tex
\section{Conclusion}

We have presented a novel unifying framework for agglomerative clustering of graphs with both positive and negative edge weights; and we have shown that several existing clustering algorithms, e.g. the Mutex Watershed, can be reformulated as special cases of one underlying agglomerative algorithm. This framework also allowed us to introduce new algorithms, one of which, based on an \emph{Average} linkage criterion, outperformed all the others: it proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
On biological images, this simple average agglomeration algorithm can represent a valuable choice for a user who is not willing to spend much time tuning complex task-dependent pipelines based on superpixels.  
% In future work, we plan to explore common theoretical properties of the algorithms included in the framework.

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Conclusion}
We have presented an unifying framework for agglomerative clustering of graphs with both positive and negative edge weights; and we have shown that some existing clustering algorithms, e.g. the Mutex Watershed, can be reformulated as special cases of this framework. 
We have analyzed several theoretical and empirical properties of the algorithms included in this framework. On instance segmentation, algorithms based on an average linkage criterion outperformed all the others: they proved to be simple and remarkably robust approaches to process short- and long-range predictions of a CNN.
 % applied to an instance segmentation task.
On biological images, these simple average agglomeration algorithms achieve state-of-the-art results without requiring the user to spend much time tuning complex task-dependent pipelines based on super-pixels.
% can represent a valuable choice for a user who is not willing to spend much time tuning complex task-dependent pipelines based on super-pixels.  
% In future work, we plan to explore common theoretical properties of the algorithms included in the framework.
% On biological images, this simple average agglomeration algorithm superpixels
